Methods

### 2019-01-23 Methods.Rmd
some_bits

SACTN_3yr <- SACTN_split %>% 
  filter(year(date) %in% seq(2015, 2016)) %>% 
  drop_na() # Removing NA values within the dataset
```

@@

>>>>

SACTN_3yr <- SACTN_split %>% 
  filter(year(date) %in% seq(2015, 2016)) %>% 
  drop_na() # Removing NA values within the dataset

save(SACTN_3yr, file = "Data/SACTN_3yr.RData")
```

@@

## CMC dataset

```{r}
CMC_Lamberts_Bay <- read_csv("Data/CMC/CMC_Lamberts Bay_SST_timeseries_5nearest.csv")
CMC_Port_Nolloth <- read_csv("Data/CMC/CMC_Port Nolloth_SST_timeseries_5nearest.csv")
CMC_Saldanha_Bay <- read_csv("Data/CMC/CMC_Saldanha Bay_SST_timeseries_5nearest.csv")
CMC_Yzerfontein <- read_csv("Data/CMC/CMC_Yzerfontein_SST_timeseries_5nearest.csv")

CMC_SST <- rbind(CMC_Lamberts_Bay,CMC_Port_Nolloth, CMC_Saldanha_Bay,CMC_Yzerfontein) %>%
  dplyr::rename(site = station)

CMC_SST$date <- (ymd(CMC_SST$date))

# save(CMC_SST, file = "Data/CMC_SST.RData")
```

```{r}
load("Data/CMC_SST.RData")

CMC_SST <- CMC_SST %>% 
  drop_na()

CMC_SST <- CMC_SST %>% 
  dplyr::rename(temp = nearest1)

insitu_CMC <- match_func(df = CMC_SST) %>%
  drop_na()
CMC_plot <- match_plot(df = insitu_CMC)

ggplot(data = insitu_CMC, aes(x = date, y = temp, colour = site)) +
geom_line(aes(group = site)) +
labs(x = "", y = "Temperature (°C)") +
theme(axis.text.x = element_text(angle = 45)) +
theme_linedraw() +
theme(legend.position = "top")
```

This code is testing out the wavelet analyses for the in situ temperature data. This is for the insitu temperature only. This plot is a wavelet analyses for all of the insitu collected data only

```{r}
load("Data/SACTN_3yr.RData")

temp.d <- SACTN_3yr %>% 
  dplyr::group_by(site, date) %>% 
  dplyr::summarise(temp = mean(insitu_temp, na.rm = T)) %>%
  dplyr::mutate(no = seq(1:n())) %>%
  dplyr::ungroup() %>% 
  dplyr::select(site, no, temp, date)

auto.arima(dplyr::filter(SACTN_3yr, site == "Port Nolloth")[, "insitu_temp"], max.p = 3, max.q = 3, stationary = FALSE, 
           seasonal = FALSE)

PN <- temp.d %>% 
  dplyr::filter(site == "Port Nolloth") %>% 
  dplyr::select(temp, -date, -site) %>% 
  dplyr::mutate(no = seq(1:n())) %>% 
  dplyr::select(no, temp)

temp.d <- temp.d %>% 
  select(site, no, temp, date)

prewhite_fun <- function(x) {
  df <- x[, 2:3]
  out <- prewhiteAR(df, order = 3, method = "mle", aic = TRUE,
             genplot = FALSE, verbose = FALSE)
  colnames(out) <- c("no", "temp")
  return(out)
  }
PN_prewhite <- as.tibble(ddply(temp.d, .(site), prewhite_fun))

ggplot(PN_prewhite, aes(x = no, y = temp)) +
  geom_hline(aes(yintercept = mean(temp)), colour = "salmon") +
  geom_line() +
  facet_wrap(~ site, nrow = 4) +
  theme_bw()

wl.fun <- function(x) {
  analyze.wavelet(x, "temp", loess.span = 0, dt = 1,
                   dj = 1/50, lowerPeriod = 2, make.pval = TRUE, n.sim = 50, 
                   method = "white.noise", verbose = FALSE)
}

PN_wave <- dlply(PN_prewhite, .(site), wl.fun)

site.names <- list("Port Nolloth", "Lamberts Bay", "Saldanha Bay", "Yzerfontein")
for (i in 1:length(PN_wave)) {
  attributes(PN_wave[[i]]) <- c(attributes(PN_wave[[i]]), ref = site.names[i])
  }

plot_fun <- function(x) {
  wt.image(x, siglvl = 0.05, col.contour = "black", color.key = "quantile",
           timelab = "Days", verbose = FALSE, useRaster = TRUE,
           periodlab = "Period", lwd = 1, graphics.reset = FALSE,
           main = attributes(x)$ref)
  }

# ... apply the function
#op <- par(no.readonly = TRUE)
par(mfrow = c(2, 2),
    mar = c(2.5, 3.5, 2.5, 0.5),
    mgp = c(2.5, 1, 0),
    oma = c(0, 0, 1, 0))
l_ply(PN_wave, plot_fun)
#par(op)

# Save each of the graph seperate- graph PN, LB, saldanha Bay and Yzerfontein
```
